\documentclass{tufte-handout}
\usepackage{expex}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{booktabs}

\title{Lesson 8: Simple past tense, what did you do on the weekend?}
\author{Stephen Lam}
\date{30 June 2014}

\newcommand{\dialt}{\smallcaps{teacher}\hspace{1em}}
\newcommand{\dials}{\smallcaps{student}\hspace{1em}}
\newcommand{\dialsone}{\smallcaps{s1}\hspace{1em}}
\newcommand{\dialstwo}{\smallcaps{s2}\hspace{1em}}
\newcommand{\dialtone}{\smallcaps{stephen}\hspace{1em}}
\newcommand{\dialttwo}{\smallcaps{tom}\hspace{1em}}
\newcommand{\dialtboth}{\smallcaps{both}\hspace{1em}}

\begin{document}

\maketitle

\begin{abstract}
\noindent By the end of this lesson, students will be able to discuss their weekend using simple past tense.
\end{abstract}

\section{Dialogue (40 min total)}
\subsection{Watch Moe's promotional video (5 min)}
\begin{enumerate}
\item What is the name of the restaurant?
\item What kind of food do they serve?
\end{enumerate}
After watching the video, ask: "Has anyone been to Moe's? I have been to Moe's."

\subsection{Weekend Trip (15 min)}
Go over the following dialogue twice. The first time have the students listen. Then let them follow along with the text the second time. The second time, show pictures of unfamiliar vocabulary.
\\
\hspace{0em}\\
It is Monday morning at Moe's.
\dialtone Hey, Tom! Good to see you again!\\
\dialttwo Hey, Stephen! How was your weekend?\\
\dialtone It was great! I visited my uncle who lives in New York.\\
\dialttwo New York? Did you take a plane?\\
\dialtone No, I took a bus. The ticket only cost me \$25.\\
\dialttwo How long was the bus ride?\\
\dialtone It was about 5 hours. On the way I slept and read magazines.\\
\dialttwo So what did you do in New York? Did you see the Statue of Liberty?\\
\dialtone I saw the Statue of Liberty from the bus window as we crossed the bridge, but I didn't get to take a tour. Instead, my uncle and I went to Broadway and watched Mary Poppins.\\
\dialttwo Nice! Were there lots of people?\\
\dialtone Yes, it was a full house. It was a fun show. I bought this T-Shirt from the gift shop as a souvenir. Oh, there's a customer.\\
\dialtboth Welcome to Moe's!\\

\begin{enumerate}
\item Where did I go over the weekend?
\item Who did I visit?
\item How did I get to New York?
\item Why did I take a bus instead of a plane? (advanced students)
\item How long was the bus ride?
\item What did I see from the bus window? (What do you see from the window?)
\item Did I take a tour of the Statue of Liberty? (Let's take a tour.)
\item What did I buy?
\item What did Stephen and Tom say at the end?
\end{enumerate}

\noindent Additional vocabulary: customer, souvenir, sold out

\subsection{What do you see from the window? (10 min)}
Have students come to the windows and explain what they see. "I see a ...".

\begin{enumerate}
\item What do you see from the window?
\item What do you see in the parking lot?
\item What do you see behind the parking lot?
\item What do you see behind that?
\end{enumerate}

Now have students return to their seats, and ask them in the past tense what they saw.

\begin{enumerate}
\item What did you see from the window?
\item What did you see in the parking lot?
\item What did you see behind the parking lot?
\item What did you see behind that?
\end{enumerate}

\subsection{Let's take a tour (5 min)}
Take a tour around church.
Additional vocabulary: tour guide

\subsection{How was your weekend?}
How was your day? How was your weekend?

\section{Regular verbs (5 min total)}
visit/visited, open/opened, close/closed, brush/brushed

\section{Irregular verbs (15 min total)}
Go over additional verbs.\\
We \textbf{say} "Cheese" when we take pictures. At the party, we \textbf{said} "Happy Birthday" to Tom.\\
We \textbf{make} burritos. Yesterday, we \textbf{made} 180 burritos.\\
We \textbf{go} to church on Sundays. We \textbf{went} to church yesterday.\\
We \textbf{take} pictures with a camera. I \textbf{took} many pictures at the wedding.\\
I \textbf{come} here every Monday to teach. Sarah \textbf{came} to the USA with her parents when she was 5 years old.\\

\begin{tabular}{ l l }
say & said\\
make & made\\
go & went\\
take & took\\
come & came\\
see & saw\\
know & knew\\
get & got\\
give & gave\\
find & found\\
leave & left\\
put & put\\
bring & brought\\
write & wrote\\
stand & stood\\
sit & sat\\
hear & heard\\
read & read\\
drive & drove\\
buy & bought\\
wear & wore\\
\end{tabular}
\end{document}
