\documentclass{tufte-handout}
\usepackage{expex}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{booktabs}

\title{Lesson 7: Simple present tense, daily life\thanks{Material in this lesson is adapted from Kenneth Beare's Absolute Beginners 20 Point Program on About.com. This lesson guide covers material from lessons 21, 22, and 23. Page numbers refer to \emph{English in Action}, 2nd ed. by Foley and Neblett.}}
\author{Stephen Lam}
\date{23 June 2014}

\newcommand{\dialt}{\smallcaps{teacher}\hspace{1em}}
\newcommand{\dials}{\smallcaps{student}\hspace{1em}}
\newcommand{\dialsone}{\smallcaps{s1}\hspace{1em}}
\newcommand{\dialstwo}{\smallcaps{s2}\hspace{1em}}

\begin{document}

\maketitle

\begin{abstract}
\noindent By the end of this lesson, students will be able to describe their daily routine in present simple tense. They will be able to answer ``when'' questions.
\end{abstract}

\section{When (24 min total)}
\subsection{Vocabulary (12 min)}
\hspace{0em}\\
7:30 - get up\\
7:40 - take a shower\\
7:45 - get dressed\\
7:50 - eat breakfast\\
8:00 - go to work/school\\
12:00 - have/eat lunch\\
5:00 - get home\\
5:30 - make/cook dinner\\
6:00 - eat dinner\\
6:30 - do the dishes\\
7:00 - do the laundry\\
7:30 - watch TV\\
8:30 - check email\\
10:30 - go to bed\\

\begin{framed}
\dialt I get up at 7:30.\\
\hspace{0em}\hphantom \dialt I take a shower at 7:40.\\
\hspace{0em}\hphantom \dialt etc\ldots
\end{framed}

\noindent Additional vocabulary:\\
walk/run/bike/drive (to work/school)\\
brush my teeth\\
comb/brush my hair\\

\subsection{Answering questions (6 min)}

\begin{framed}
\dialt \textbf{When} do you \textbf{get up}?\\
\hspace{0em}\hphantom \dialt I \textbf{get up} at 7:30.\\
\end{framed}

\subsection{Adding he/she (6 min)}
\begin{framed}
\dialt \textbf{When} does he \textbf{get up}?\\
\hspace{0em}\hphantom \dialt He \textbf{gets up} at 7:30.\\
\dialt \textbf{When} does he \textbf{have breakfast}?\\
\hspace{0em}\hphantom \dialt He \textbf{has breakfast} at 8:00.\\
\end{framed}
Alternate between a question with ``you'' and ``he/she''. Emphasize the conjugated verb suffix `-s'.
\ex
\dialt Francisco, when do you have breakfast?\\
\dialsone I have breakfast at eight o'clock.\\
\dialt Cecilia, when does he have breakfast?\\
\dialstwo He has breakfast at eight o'clock.\\
\xe

\section{Asking questions (25 min total)}
\subsection{(15 min)}
\begin{framed}
\dialt Stephen, when \textbf{do} you get up?\\
\dialt I get up at seven o'clock.\\
\dialt Stephen, when \textbf{\underline{does}} Francisco get up?\\
\dialt Francisco get\textbf{\underline{s}} up at seven o'clock.\\
\end{framed}

Have students ask each other.

\subsection{Exercise (10 min)}
Each student asks his partner two questions, and then reports to the class about himself and his partner.

\section{Stretch Break! (2 min total)}

\section{Textbook Exercises (30 min total)}
147A - Quickly go over the chart at the top of 147. Write at, on, in, from/to on the board. Read the questions and have the students answer orally.\\
148A, B, C (orally)\\
152 (go over the following vocabulary before listening to the dialog):\\
sophomore, alarm clock, turn off, talk on the phone, play video games, set the alarm

\end{document}
