\documentclass{tufte-handout}
\usepackage{expex}
\usepackage{hyperref}
\usepackage{framed}

\title{Lesson 5: Clothing, ``There is'', ``There are'', Adjectives\thanks{Material in this lesson is adapted from Kenneth Beare's Absolute Beginners 20 Point Program on About.com. This lesson guide covers material from lessons 14 to 16. Page numbers refer to \emph{English in Action}, 2nd ed. by Foley and Neblett.}}
\author{Stephen Lam}
\date{9 June 2014}

\newcommand{\dialt}{\smallcaps{teacher}\hspace{1em}}
\newcommand{\dials}{\smallcaps{student}\hspace{1em}}
\newcommand{\dialsone}{\smallcaps{s1}\hspace{1em}}
\newcommand{\dialstwo}{\smallcaps{s2}\hspace{1em}}

\begin{document}

\maketitle

\begin{abstract}
\noindent By the end of this lesson, students will know basic clothing vocabulary. They will be able to identify objects in a picture using \emph{there is} and \emph{there are}.
\end{abstract}

\section{Clothing (25 min total)}
\subsection{Vocabulary (10 min)}
\marginnote[2.8em]{While pointing to various articles of clothing on page 128 or objects in the classroom. Alternate between \emph{this} and \emph{that} when using classroom objects.}
\ex
\dialt \textbf{Repeat after me.} This is a shirt.\\
\dials This is a shirt.\\
\dialt These are pants.\\
\dials These are pants.\\
\emph{etc\ldots}
\xe

\subsection{Asking questions with \emph{this} and \emph{that} (15 min)}
Model then ask individual students:
\ex
\dialt Tom, is this a belt? (\emph{point to picture})\\
\dials Yes, that is a belt.
\xe
\ex
\dialt Tom, is this a suit? (\emph{point to picture})\\
\dials No, that isn't a belt. that is a suit.
\xe

Students ask each other (give the asker a picture).

\section{``There is'' and ``There are'' (25 min total)}
\subsection{``Is there...'' (10 min)}
\begin{framed}
\dialt \textbf{Is there} a car in this picture?\\
\hspace{0em}\hphantom \dialt Yes, \textbf{there is} a car in that picture.\\
\dialt \textbf{Is there} a book in this picture?\\
\hspace{0em}\hphantom \dialt No, \textbf{there isn't} a book in that picture.
\end{framed}

Ask individual students. Also, combine with prepositions of location if appropriate: ``Is there a book on the table?'' Alternate these objects with objects in the classroom so that the difference between ``this'' and ``that'' is reinforced.

\subsection{``Are there four...'' (10 min)}
\begin{framed}
\dialt \textbf{Are there} three cars in this picture?\\
\hspace{0em}\hphantom \dialt Yes, \textbf{there are} three cars in that picture.\\
\dialt \textbf{Are there} two books in this picture?\\
\hspace{0em}\hphantom \dialt No, \textbf{there aren't} two books in that picture.
\end{framed}

Ask individual students.

\subsection{Asking questions (5 min)}
Have students ask each other. Give the asker a picture.

\section{Stretch Break! (2 min total)}
Use this time also to mention body part names (``head'', ``neck'', ``arms'', ``fingers'') as each part is stretched. At the end, careful listeners will be rewarded with candy.

\section{Adjectives (30 min total)}
\marginnote[2.8em]{Point to two illustrations that show similar objects in different states.}
\begin{framed}
\dialt This is an \textbf{old} car. This is a \textbf{new} car.\\
\dialt This is an \textbf{old} hat. This is a \textbf{new} hat.\\
\dialt This is an \textbf{old} house. This is a \textbf{new} house.\\
\dialt This is an \textbf{old} man. This is a \textbf{young} man.\\
\dialt This is an \textbf{old} woman. This is a \textbf{young} woman.\\
\dialt This is a \textbf{big} hat. This is a \textbf{small} hat.\\
\dialt This is a \textbf{big} book. This is a \textbf{small} book.\\
\dialt This is a \textbf{beautiful} city. This is an \textbf{ugly} city.\\
\dialt These are \textbf{beautiful} sandals. These are \textbf{ugly} shorts.\\
\dialt This is a \textbf{thick} book. This is a \textbf{thin} book.\\
\dialt These are \textbf{thick} socks. These are \textbf{thin} socks.\\
\dialt These are \textbf{cheap} shoes. These are \textbf{expensive} shoes.\\
\dialt This is an \textbf{empty} box. This is a \textbf{full} box.\\
\dialt This is an \textbf{empty} cup. This is a \textbf{full} cup.\\
\end{framed}

\ex
Ask individual students:\\
\dialt What is this? (\emph{point to picture})\\
\dials That is an old house.
\xe

Have students ask each other.

\end{document}
